Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
intro

We describe and evaluate two approaches for synthesising digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}.

@@

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}

We provide experimental results 
showing that both approaches are able to efficiently synthesise stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
from a transfer function representation into a state space representation. 
Such representation allows to study the  input-to-state dynamics, while 
transfer functions represents only input-output relations and cannot be 
enough to ensure deeper properties, e.g. the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
safety properties, that is only  possible in state-space representation. 
In addition to the already existing stability conditions which is a much 
harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase speed whilst retaining
  soundness.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

We describe and evaluate two approaches for synthesizing digital controllers
for state-space physical plants, both based on CounterExample
Guided Inductive Synthesis (CEGIS)~\cite{sketch}, performed considering deviations due the computation computations and representations of dynamics, providing sufficient conditions for sound and complete solutions.

@@

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
%\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}

We provide experimental results 
showing that both approaches are able to efficiently synthesize stable and safe controllers 
for a set of intricate physical plant models taken from the digital 
control literature: the median runtime for our benchmark
set is \textcolor{red}{$XXX$}s, i.e., most controllers can be synthesized in less
than \textcolor{red}{$XXX$} seconds.

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space representation. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g. the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
  safety properties, that is only  possible in state-space representation. 
  In addition to the already existing stability conditions which is a much 
  harder problem.
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound and 
  complete synthesis of state feedback systems considering the various
  errors sources in the implementation of control algorithm and in the
  computational modeling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
